Bird beak's elaboration and innovation

### 2022-03-02 Analysis/10-Figure1.Rmd
Update 10-Figure1.Rmd
Looks alright

    ## Empty plot
    par(bty = "n")
    plot(NULL, xlim = c(0,1.5), ylim = c(0,lim_up), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

@@

    ## Add the y axis
    axis(4, at = seq(from = 0, to = lim_up, by = 5), labels = seq(from = 0, to = lim_up, by = 5), las = 2)

@@

## Global window
lay_mat_order <- rbind(
        matrix(c(1,1, 2:9), ncol = 10, nrow = 1), # line 1
        matrix(c(1,1, 10:17), ncol = 10, nrow = 1), # line 2
        matrix(c(1,1, 18:25), ncol = 10, nrow = 1), # line 3
        matrix(c(26:35), ncol = 10, nrow = 1), # line 4
        matrix(c(36:45), ncol = 10, nrow = 1), # line 5
        matrix(c(46:55), ncol = 10, nrow = 1) # line 7
    )
lay_mat_super <- rbind(
        matrix(c(1,1, 2:9), ncol = 10, nrow = 1), # line 7
        matrix(c(1,1, 10:17), ncol = 10, nrow = 1) # line 8
    )

# sequence <- c(c(rep(2, 3), 3), c(rep(4, 3), 5), c(rep(6, 3), 7), c(rep(8, 3), 9))

layout_matrix <- layout(rbind(lay_mat_super, (lay_mat_order+17)))

>>>>

    ## Empty plot
    par(bty = "n")
    plot(NULL, xlim = c(-0.5,1.5), ylim = c(0,lim_up), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

@@

    ## Add the y axis
    axis(2, at = seq(from = 0, to = lim_up, by = 5), labels = seq(from = 0, to = lim_up, by = 5), las = 2)

@@

## Global window
lay_mat_order <- rbind(
        matrix(c(1,1, 2:9), ncol = 10, nrow = 1), # line 1
        matrix(c(1,1, 10:17), ncol = 10, nrow = 1), # line 2
        matrix(c(1,1, 18:25), ncol = 10, nrow = 1), # line 3
        matrix(c(26:35), ncol = 10, nrow = 1), # line 4
        matrix(c(36:45), ncol = 10, nrow = 1), # line 5
        matrix(c(46:55), ncol = 10, nrow = 1) # line 6
    )
lay_mat_super <- rbind(
        matrix(c(1,1, 2:9), ncol = 10, nrow = 1), # line 7
        matrix(c(1,1, 10:17), ncol = 10, nrow = 1) # line 8
    )

heights_vals <- rep(1, 9)
widths_vals <- rep(c(1, 1/3), 5)
layout_matrix <- layout(rbind(lay_mat_super, (lay_mat_order+17)), widths = widths_vals, heights = heights_vals, respect = TRUE)
